% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black 
    %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{{\LARGE Bihan Jiang}} & \href{mailto:bhj09@imperial.ac.uk}{bhj09@imperial.ac.uk}\\
	%{\footnotesize \texttt{\colorbox{yellow}{[web version:  address \& phone omitted]}}} & \href{www.doc.ic.ac.uk/~bhj09}{www.doc.ic.ac.uk/~bhj09} \\
{ \texttt{{180 Queen's Gate, Imperial College London, UK. SW7 2RH}}} & {+447861457507} \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
%\begin{comment}
\resheading{Research Interests}
{\small
\begin{itemize}
\item \textbf{Machine learning:} Support Vector Machines; Artificial Neural Networks; Hidden Markov Models (HMMs); Regression; Clustering; Bayesian inference; Dimensionality reduction algorithms; Deep learning 

\item \textbf{Feature extraction:} Gabor filters; Local Binary Patterns (LBPs); Local Phase Quantization (LPQ); Scale-invariant Feature transform (SIFT); spatio-temporal extensions of texture descriptors  
 
\item \textbf{Automatic human (facial) behaviour analysis:} Emotion recognition; facial action unit recognition; affective analysis (i.e. valence/arousal); spatio-temporal alignment; social signal processing 
\end{itemize}
}
%\end{comment}

\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{{Imperial College London}}{London, UK}{{PhD in Computer Science}; }{Oct. 2010 -- Oct. 2014 (expected)}
				{ \small
				\begin{itemize}
					\resitem{Research focus: developing and applying computer vision and pattern recognition approaches to automatic human (social) behaviour analysis, in particular facial expression analysis }
					\resitem{Thesis title: Spatial and temporal analysis of facial actions }

					\resitem{To date there are \textbf{7} papers published and presented at conferences and journals which have led to more than \textbf{200} citations (according to Google Scholar) } 
				\end{itemize}
				}
		\item
			\ressubheading{{Imperial College London}}{London, UK}{{MSc in Computing Science}; Distinction (76.7\%) }{Oct. 2009 -- Sept 2010}
				{ \small
				\begin{itemize}
				\resitem{Main Modules: Object-Orientated Programming, Machine Learning, Concurrency, Databases, Software Engineering and Computer Systems}
				\resitem{Thesis title: A comparison and investigation of dense temporal appearance descriptors for AU analysis}
				\end{itemize}
				}
		\item
			\ressubheading{{University of Central Lancashire}}{Preston, UK}{{BEng in Digital Signal \& Image Processing}; First class (86\%) }{Sept. 2006 -- May 2009}
				{ \small
				\begin{itemize}
				\resitem{Main modules: Data Communication, Digital Signal Processing, Digital Image Processing, Artificial Neural Networks, Computer Vision and Mathematics}
				\resitem{Thesis title: A real-time system for automatic emotion recognition}
				\resitem{Ranked 1st out of 73 students on the course}
				\end{itemize}
				}
	\end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{itemize}
		\item 
			\ressubheading{{Imperial College London}}{London, UK}
				{Research assistant}{Oct. 2010 -- Present}
				{ \small
				\begin{itemize}
					%\resitem{Proposed a novel feature extraction method which can capture spatio-temporal appearance changes}
					%\resitem{Detected temporal dynamics of facial actions using a hybrid of SVMs and HMMs }
					%\resitem{Proposed a novel paramatric temporal warping alorithm for temporal alignment of facial behaviours }
					%\resitem{Designed a baseline system for the Facial Expression Recognition and Analysis Challenge (FERA2011) and the Continuous Audio/Visual Emotion and Depression Recognition Challenge (AVEC2013)}
				
					\resitem{Employed by European Commission on the Social Signal Processing Network (SSPNet) project and British Research Council on the Analysis of Facial Behaviour for Security in 4D (4D-FAB) project}
					\resitem{Developed tools in MATLAB and C++ for automatic facial behaviour analysis}
					\resitem{4D Facial Expression Database processing and FACS annotation}
					%\resitem{Published and presented (oral or poster) a number of high quality conference and journal papers}

					\resitem{Attended the MIT-Imperial Collaborative Research Development Course}
					\resitem{Attended the Facial Action Coding System (FACS) workshop (by Erika Rosenberg)}
				\end{itemize}
				}

			\ressubsubheading{Teaching assistant}{Oct. 2011 -- present}
				{ \small
				\begin{itemize}
					\resitem{Tutorial helping, marking and invigilation for various undergraduate and postgraduate modules such as Machine Learning and Software Engineering}
					\resitem{Lab demonstrator for C++, Java and MATLAB}
				\end{itemize}
				}

			\ressubsubheading{MSc group project}{Mar. 2010 -- Sept. 2010}
				{ \small
				\begin{itemize}
					\resitem{Used a high-precision 3D location tracking system provided by Ubisense to create an audio-visual interactive art installation which encouraged human-human interaction}
					\resitem{Implemented in C\# (Ubisense) and Java, and built a connection between them via socket}
					\resitem{Worked in a team and interacted with client (a Danish artist Tine Bech)}
				\end{itemize}
				}

		\item			
			\ressubheading{Oregon State University}{Corvallis, OR}{Visiting scholar}{Jul. 2013 -- Oct. 2013}
				{ \small			
				\begin{itemize}
					\item Applied novel deep learning techniques to facial expression analysis
					\item Implemented machine learning techniques in MATLAB and Java
				\end{itemize}
				}
	
%		\item			
%			\ressubheading{Entrepreneurial Experience}{Billings, MT}{On Site Computer Tech Support}{Jan. 2004 -- May 2005}
%				{ \footnotesize				
%				\begin{itemize}
%					\item Initiated a freelance computer tech support business which provided the community with affordable, on-site computer service, consultation, and training
%				\end{itemize}
%				}

	\end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
\resheading{Leadership \& Activities                                                                                          }
	\begin{itemize}
		\item 
			\ressubheading{{Imperial College London}}{London, UK}
				{Project leader -- Bubble tea commercial project}{Oct.~2011 -- Oct.~2012}
				{ \small
				\begin{itemize}
					\resitem{Collaborated with the Imperial College catering team to allow the sale of bubble tea on campus}
					\resitem{Conducted market research to understand the demand for the bubble tea  }
					%\resitem{Proposed marketing plans to build customer awareness and grow sales}
				\end{itemize}
				}

			\ressubsubheading{Sponsorship Liaison Team leader -- ICCA Drama society}{Oct.~2010 -- Mar.~2011}
				{ \small
				\begin{itemize}
					\resitem{Led a team of 10 people and fundraised more than £1000 sponsorship }
					\resitem{Identified potential funding sources, worked closely with the marketing and finance team to prepare necessary material (e.g., brochure and budge plan), and distributed tasks to team members }
				\end{itemize}
				}

			\ressubsubheading{Committee member -- Imperial Consulting Group}{Oct.~2012 -- Mar.~2013}
				{ \small
				\begin{itemize}
					\resitem{One of the founding members of the Imperial Consulting Group}
					\resitem{Involved with the setup of the group including website development, logo design and project hunting}
				\end{itemize}
				}
	
	\ressubsubheading{Volunteer -- IntoUniversity}{Oct.~2010 -- Jun.~2011}
				{ \small
				\begin{itemize}
					\resitem{Acted as a role model, supported academic progress and provided inspiration and encouragement to young people for whom university education is not necessarily a common expectation}
					
				\end{itemize}
				}

		\item			
			\ressubheading{University of Central Lancashire}{Preston, UK}{Course representative}{Oct.~ 2006 -- July.~2009}
				{ \small			
				\begin{itemize}
					\item Acted as liaison between course peers and various staffs
					\item Coordinated and presented essential feedback to the university
				\end{itemize}
				}
	
%		\item			
%			\ressubheading{Entrepreneurial Experience}{Billings, MT}{On Site Computer Tech Support}{Jan. 2004 -- May 2005}
%				{ \footnotesize				
%				\begin{itemize}
%					\item Initiated a freelance computer tech support business which provided the community with affordable, on-site computer service, consultation, and training
%				\end{itemize}
%				}

	\end{itemize}  % End Experience list
\end{comment}

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%\begin{comment}
\resheading{{Publications}}
%\vspace{1cm}
\textit{Journal articles:}
	\begin{itemize}
{ \small
\item \textbf{Bihan Jiang}, Brais Martinez, Michel F. Valstar, and Maja Pantic, Automatic Analysis of Facial Actions: A Survey, International Journal of Computer Vision, under review, 2014 (IF2012 3.623). 

\item \textbf{Bihan Jiang}, Michel Valstar, Brais Martinez, and Maja Pantic, A Dynamic Appearance Descriptor Approach to Facial Actions Temporal Modelling, IEEE Transactions on Cybernetics, 2014 (IF2012: 3.236).

\item Michel F. Valstar, Marc Mehu, \textbf{Bihan Jiang}, Maja Pantic and Klaus Scherer. Meta-Analysis of the first Facial Expression Recognition Challenge, IEEE Transactions on Cybernetics, 42(4), 2012 (IF2012: 3.236). 
}
\end{itemize}
\textit{Conference papers:}
	\begin{itemize}
{ \small
\item \textbf{Bihan Jiang}, Brais Martinez, and Maja Pantic, Parametric temporal alignment for the detection of facial action temporal segments, British Machine Vision Conference, accepted, 2014. 

\item \textbf{Bihan Jiang}, Brais Martinez, Michel F. Valstar, and Maja Pantic, Decision Level Fusion of Domain Specific Regions for Facial Action Recognition, Proc. Int'l Conf. Pattern Recognition, 2014.

\item Michel F. Valstar, Bjorn Schuller, Kirsty Smith, Florian Eyben, \textbf{Bihan Jiang}, etc,  'AVEC 2013 - The Continuous Audio/Visual Emotion and Depression Recognition Challenge', Proc. Int'l Conf. ACM Multimedia, 2013
\item \textbf{Bihan Jiang}, Michel F. Valstar, and Maja Pantic, Facial Action Recognition using sparse appearance descriptors and their pyramid representations, proc. ASE/IEEE Int'l conf on Social Computing, 2012. 
\item \textbf{Bihan Jiang}, Michel F. Valstar, and Maja Pantic, Action Unit detection using sparse appearance descriptors in space-time video volumes, Proc. Int'l Conf. Face and Gesture Recognition, pp. 314 - 321, 2011.
\item Michel F. Valstar, \textbf{Bihan Jiang}, Marc Méhu, Maja Pantic, and Klaus Scherer, The First Facial Expression Recognition and Analysis Challenge, Proc. Int'l Conf. Face and Gesture Recognition, pp. 921 - 926, 2011.
}	
\end{itemize}
%\textit{Papers under review:}
%\begin{itemize}
%{ \small

%}
%\end{itemize}
%\end{comment}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{{Skills}}
	\begin{description}
{\small
		\item[Languages:] {Fluent in English and Cantonese, Native in Mandarin}
		\item[Technologies:] {  MATLAB, C++, Java,
			Prolog, MySQL, HTML, CSS, SVN, Git
		}
		\item[Libraries:] { OpenCV, Boost, Eigen, libsvm, spider			
		}
}
	\end{description} % End Skills list


%\begin{comment}
\resheading{Academic services
                                                                              }
{\small
	\begin{description}
		\item[Journal review:] \mbox{}\\
				%\textbf{Journal review:}\\ 
			\vspace{-0.2cm}
			\begin{itemize}
			\item 	Journal of Machine Vision and Applications; 
			\end{itemize}
		\vspace{-0.2cm}
	    \item[Program committee:] \mbox{}\\
	    			\vspace{-0.2cm}
			\begin{itemize}
			\item British Machine Vision Conference 2014
			\item ACM International Conference on Multimodal Interaction 2013, 2014
			%\item IEEE International Conference on Multimedia and Expo 2013
			\end{itemize}
	\end{description}  % End Experience list
}
%\end{comment}

\begin{comment}
\resheading{Leadership \& Activities     
                                                                              }
{\small
	\begin{description}
		\item[Student societies:] Imperial College Consultancy Society; Imperial College Chinese Drama Society; Imperial College SIFE society;
		\item [Volunteers:] PDSA charity organisation; IntoUniversity;  
	\end{description}  % End Experience list
}
\end{comment}

%\begin{comment}
\resheading{Collaborators}

\begin{description}
{\small
\item {MSc/PhD supervisor: \textbf{Prof.~Maja Pantic}, Imperial College London}

\item {Research mentor:  \textbf{Dr.~Michel Valstar}, University of Nottingham}
%\item {Research mentor: \textbf{Dr.~Brais Martinez}, Imperial College London}
\item {Summer placement mentor: \textbf{Dr.~Sinisa Todorovic}, Oregon State University}
\item {BEng project supervisor: \textbf{Prof.~Bogdan J. Matuszewski}, University of Central Lancashire}
}
\end{description}

%%%%%%%%%%%%%%%%%%%%%

%\end{comment}
\end{document}



